---
title: "RA_R"
author: "Tsering Sherpa"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(dplyr)
library(lubridate)
library(fuzzyjoin)
library(stringdist)
library(data.table)
library(stringr)
library(purrr)
library(uuid)
library(pcaMethods)
library(tibble)
```
Load in Data:
```{r}
#htn_schools <- read.csv("file_path_name/htn_schools.csv")
```

Summary Statistics Needed:
Total Number of schools
Total Number of Schools with a computer lab
Average exam score (subject specific and cumulative) for schools with computer labs and schools without computer labs.
Average exam score (subject specific and cumulative) for schools with computer labs and schools without computer labs by gender.
Average exam score (subject specific and cumulative) for schools with computer labs and schools without computer labs by grade and year.
Number of students per grade
Number of students per grade in computer vs non computer lab schools
Standard deviations



